% HMC Math dept HW template example
% v0.04 by Eric J. Malm, 10 Mar 2005
\documentclass[10pt,a4paper,boxed]{hmcpset}

% set 1-inch margins in the document
% \usepackage[margin=1in]{geometry}
\usepackage{enumerate}
\usepackage{todonotes}
%\usepackage{tikz}
%\usetikzlibrary{positioning}
\usepackage{subfig} % subfigures in figures.	
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

%% work around for subfig and asy environment
\makeatletter
\newsavebox{\sfe@box}
\newenvironment{subfloatenv}[2]{%
\def\sfe@caption{#1}%
\def\sfe@label{#2}%
\setbox\sfe@box\hbox\bgroup\color@setgroup}%
{\color@endgroup\egroup\subfloat[\sfe@caption]%
{\usebox{\sfe@box}\label{\sfe@label}}}
\makeatother

% include this if you want to import graphics files with /includegraphics
\usepackage{graphicx}

\renewcommand*{\familydefault}{\sfdefault}
\newcommand{\vect}[1]{\mathbf{#1}}


%\tikzset{node distance=2cm, inner/.style={draw,circle}, leaf/.style={draw,rectangle}}

\usepackage{hyperref}

% info for header block in upper right hand corner
\name{Lukas Gesing, Patrick Kaster}
\class{MA-INF 4201 - Artificial Life}
\assignment{Exercise Sheet 3}
% \duedate{09/03/2004}

\begin{document}
\begin{problem}[Assignment 16]
\end{problem}
\begin{solution}
The rule has a silent state, if a dead cell is has no neighbours. I wouldn't characterize it as totalistic, without having specified some kind of binary value to the neighbouring cells. It is symmetric though, since the 23/3 rule doesn't depend on the position of the neighbours. So each symmetric configuration will lead to the same result. It is legal, since it is symmetric and shows a silent state. It is not peripheral, since the outcome is in any case dependent on whether the cell os dead or alive.
\end{solution}


\begin{problem}[Assignment 17]
\end{problem}
\begin{solution}
That it is possibly to create a Game of Life pattern that can grow infinitely.
\end{solution}


\begin{problem}[Assignment 18]
\end{problem}
\begin{solution}
Class IV. It's evolution leads to complex structures, even releasing a glider at some point of it's evolution, and the \emph{r-pentomino} is long lived.
\end{solution}

\end{document}
